---
title: "Lab4"
author: "alex dukart"
date: "2023-06-26"
output: html_document
---

```{r}
setwd("C:/Users/1hanv/OneDrive/Documents/EE5373/Lab4")
processors <- read.csv("all-data.csv")
#set your directory here


################################################################
#
# This function returns the data from the desired column.
# Example:  clock<-get_column("Fp2000","Processor.Clock..MHz.")

get_column <- function(x,y) {

# x = string with the name of the desired benchmark
# y = desired column
#
# Find the indices of all rows that have an entry for the  
# indicated benchmark
benchmark <- paste(paste("Spec",x,sep=""),"..average.base.",
	sep="")
ix <- !is.na(processors[,benchmark])
return(processors[ix,y])
}
################################################################




################################################################
# This function extracts the interesting data columns for the given benchmark
# program and returns a dataframe with these columns.

extract_data <- function(benchmark) {

temp <- paste(paste("Spec",benchmark,sep=""),"..average.base.", sep="")

# perf = the performance reported in the database
perf <- get_column(benchmark,temp)

#nperf = performance normalized to the overall range
max_perf <- max(perf)
min_perf <- min(perf)
range <- max_perf - min_perf
nperf <- 100 * (perf - min_perf) / range

clock <- get_column(benchmark,"Processor.Clock..MHz.")
threads <- get_column(benchmark,"Threads.core")
cores <- get_column(benchmark,"Cores")
TDP <- get_column(benchmark,"TDP")
transistors <- get_column(benchmark,"Transistors..millions.")
dieSize <- get_column(benchmark,"Die.size..mm.2.")
voltage <- get_column(benchmark,"Voltage..low.")
featureSize <- get_column(benchmark,"Feature.Size..microns.")
channel <- get_column(benchmark,"Channel.length..microns.")
FO4delay <- get_column(benchmark,"FO4.Delay..ps.")
L1icache <- get_column(benchmark,"L1..instruction...on.chip.")
L1dcache <- get_column(benchmark,"L1..data...on.chip.")
L2cache <- get_column(benchmark,"L2..on.chip.")
L3cache <- get_column(benchmark,"L3..on.chip.")

return(data.frame(nperf,perf,clock,threads,cores,TDP,transistors,dieSize,voltage,featureSize,channel,FO4delay,L1icache,L1dcache,L2cache,L3cache))

}
int95.dat <- extract_data("Int1995")
fp95.dat <- extract_data("Fp1995")
int06.dat <- extract_data("Int2006")
fp06.dat <- extract_data("Fp2006")

```

int95 I chose most of the variables but got rid of enough to have greater than 50 datapoints. I also removed the variables that have constant values.

Read this is you want to understand why backward selection with pvals is kind of bad. <https://mattkcole.com/2017/01/22/the-problem-with-backward-selection/>

```{r}
library(MASS)
int95 <- int95.dat
int95 <- int95[,-c(1,4,5,6,15,16)]
dataint95 <- na.omit(int95)
dataint95$sqrtcache <- sqrt(dataint95$L1icache)
md1 <- lm(perf~.,data=dataint95)
stepAIC(md1,direction='backward')

int06 <- int06.dat
int06 <- int06[,-c(1,4,5,6,15,16)]
dataint06 <- na.omit(int06)
dataint06$sqrtcache <- sqrt(dataint06$L1icache)
md1 <- lm(perf~.,data=dataint06)
stepAIC(md1,direction='backward')

fp95 <- fp95.dat
fp95 <- fp95[,-c(1,4,5,6,15,16)]
datafp95 <- na.omit(fp95)
datafp95$sqrtcache <- sqrt(datafp95$L1icache)
md1 <- lm(perf~.,data=datafp95)
stepAIC(md1,direction='backward')

fp06 <- fp06.dat
fp06 <- fp06[,-c(1,4,5,6,15,16)]
datafp06 <- na.omit(fp06)
datafp06$sqrtcache <- sqrt(datafp06$L1icache)
md1 <- lm(perf~.,data=datafp06)
stepAIC(md1,direction='backward')
```

```{r}
pairs(dataint95)

pairs(dataint06)

pairs(datafp95)

pairs(datafp06)
```

The resulting model is

#perf \~ clock + voltage + sqrtcache#

```{r}
fmod <- lm(perf ~ clock + voltage + sqrtcache,data=dataint95)
plot(fmod)

imod <- lm(perf ~ clock + voltage + sqrtcache,data=dataint06)
plot(imod)

smod <- lm(perf ~ clock + voltage + sqrtcache,data=datafp95)
plot(smod)

lmod <- lm(perf ~ clock + voltage + sqrtcache,data=datafp06)
plot(lmod)
```

```{r}
summary(fmod)

summary(imod)

summary(smod)

summary(lmod)
```
I had picked the three predictors since those are the 3 most commonly advertised when looking at CPU stats.

1.  Linear relationship

From the scatterplot pairs plot above we can see that the relationship is (approximately) linear for most.

2.  Normality

QQplot shows that we might have a problem with the normality of our datapoints. But it looks decent.

3.  Multicollinearity

The pairs function shows that we might have correlation between a few of our variables.

4.  Homoskedacity

Normally distributed but maybe constant variance assumption is violated. Non constant variance.
