---
title: "Lab3"
author: "Vincent Han"
date: "2023-06-14"
output: html_document
---

```{r}
crab <- read.table("crab.txt",header=TRUE)
nbadf <- read.csv("nbaplayersdraft.csv")
md1 <- lm(satell~width,data=crab)
#comments here#
resid(md1)
plot(crab$width,crab$satell)
abline(md1)
summary(md1)
plot(md1)
```

Assumption 1

Linear relationship

```{r}
plot(crab$width,crab$satell)
```

What we are looking for,

```{r}
plot(nbadf$points,nbadf$assists)
```

What we are NOT looking for,

```{r}
x = c(1,2,3,4,5,6,7,8,9,10)
y  = x^4 + rnorm(10,sd=3)
plot(x,y)
```

Assumption 2

Normally distributed errors 



(good example of normality of errors assumption failing)


```{r}
plot(md1)
```

What we are looking for,

```{r}
x1 <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20)
y1 <- 3*x1 + rnorm(20)
md3 <- lm(y1~x1)
plot(md3)
```


What we are not looking for,

bad qq plot

```{r}
md2 <- lm(y~x)
plot(md2)
```


Assumption 3

Constant errors (no patterns)


```{r}
plot(md1)
```
what we are looking for,



```{r}
plot(md3)
```





What we are not looking for,

```{r}
md2 <- lm(y~x)
plot(md2)
```

silly example

```{r}
library(rlang) 
library(alr4) 
Rpdata
mdd <- lm(y ~ x1 + x2 + x3 + x4 + x5 + x6, data=Rpdata)
summary(mdd)
plot(lm(y ~ x1 + x2 + x3 + x4 + x5 + x6, data=Rpdata))
```



Assumption 4


No outliers


```{r}
plot(crab$width,crab$satell)
```




What we are looking for

```{r}
plot(x1,y1)
```


What we are not looking for

```{r}
setwd("/Users/alexanderdukart/Downloads")
train <- read.csv("train.data.csv")
zips <- factor(train$zipcode,labels = unique(train$zipcode))
model1 <- lm(price ~ bedrooms + bathrooms + sqft_living + sqft_lot, data=train)
summary(model1)
traintest <- train
for (i in unique(train$zipcode)){
   traintest[traintest == i] <- toString(i)
}

plot(traintest$sqft_living,log(traintest$price))
mod <- lm(log(price)~sqft_living,data=traintest)
plot(mod)
```






