---
title: "lab7-han"
author: "Vincent Han"
date: "2023-07-29"
output: html_document
---

```{r}

library(dplyr)

  house_data <- read.csv("kc_house_data.csv")

  predictor_variables <- c("bedrooms", "bathrooms", "sqft_living", "sqft_lot", "floors", "waterfront", "view", "condition", "grade", "sqft_above", "sqft_basement", "yr_built", "yr_renovated", "zipcode", "lat", "long", "sqft_living15", "sqft_lot15")
  X <- house_data[, predictor_variables]
  y <- house_data$price
  
  backward_elimination <- function(X, y, threshold = 0.6) {
    initial_model <- lm(y ~ ., data = cbind(y, X))
    max_p_value <- max(summary(initial_model)$coefficients[-1, "Pr(>|t|)"])
    
    while (max_p_value > threshold) {
      remove_variable <- which(summary(initial_model)$coefficients[-1, "Pr(>|t|)"] == max_p_value)
      X <- X[, -remove_variable]
      initial_model <- lm(y ~ ., data = cbind(y, X))
      max_p_value <- max(summary(initial_model)$coefficients[-1, "Pr(>|t|)"])
    }
    
    return(initial_model)
  }
  
  final_model <- backward_elimination(X, y, threshold = 0.6)
  
  summary(final_model)
  
  
```


PART 1

```{r}
library(ggplot2)

test_data$Predicted_Price <- predict(final_model, newdata = test_data)
test_data$Percent_Error <- abs(100 * (test_data$Predicted_Price - test_data$price) / test_data$price)

q_values <- c(0.01, 0.05, 0.10, 1.0)

for (q in q_values) {
  sampled_errors <- test_data[sample(nrow(test_data), round(q * nrow(test_data))), ]
  
  p <- ggplot(data = sampled_errors, aes(x = long, y = lat)) +
    geom_point(aes(color = Percent_Error, size = price), alpha = 0.7) +
    scale_color_gradient(low = "blue", high = "red") +
    labs(title = paste("Fraction q =", q),
         x = "Longitude",
         y = "Latitude",
         color = "Percent Error",
         size = "Price") +
    theme_minimal()
  
  print(p)
}


```

I had changed the colors to blue and red since it is easier for me to see. It seems like the smaller the dot, the more red it is meaning the higher error.But honestly, most of them seem pretty blue, but there are not noticeable red ones but when they are red they are small. Meaning lower priced houses.


Problem 2

library(ggplot2)
library(gganimate)
library(gifski)

test_data$Predicted_Price <- predict(final_model, newdata = test_data)
test_data$Percent_Error <- abs(100 * (test_data$Predicted_Price - test_data$price) / test_data$price)

q_values <- c(0.01, 0.05, 0.10, 1.0)

for (q in q_values) {
  sampled_errors <- test_data[sample(nrow(test_data), round(q * nrow(test_data))), ]
  
  p <- ggplot(data = sampled_errors, aes(x = long, y = lat)) +
    geom_point(aes(color = Percent_Error, size = price), alpha = 0.7) +
    scale_color_gradient(low = "blue", high = "red") +
    labs(title = paste("Fraction q =", q),
         x = "Longitude",
         y = "Latitude",
         color = "Percent Error",
         size = "Price") +
    theme_minimal()
  
  print(p)
  
  map_with_animation <- p + transition_time(yr_built) + ggtitle('Year: {frame_time}')
  num_years <- max(test_data$yr_built) - min(test_data$yr_built) + 1
  animate(map_with_animation, nframes = num_years)
}

Something isn't working here

```{r}
house_data <- read.csv("kc_house_data.csv")

sorted_data <- house_data %>% arrange(as.numeric(zipcode))

grouped_data_list <- sorted_data %>% group_split(zipcode)

calculate_error <- function(df) {

  predictors <- c("bedrooms", "bathrooms", "sqft_living", "sqft_lot", "grade", "yr_built", "price")
  model_data <- df %>% select(all_of(predictors))

  model <- lm(price ~ ., data = model_data)
  
  predicted_prices <- predict(model, newdata = model_data)
  

```

